---
title: My dynamic report
output: html_fragment
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo=FALSE, message=FALSE, warning=FALSE, error=FALSE)
library(tidyverse)
```

```{css}
body {
    font-family: Arial, sans-serif;
    margin: 30px;
  }
  h2 {
    color: red;
  }
  p {
    font-size: 16px;
  }
```

## Car Brand & Color Observations (Auckland Roads 2025)

This dynamic report shows observational data collected from Auckland roads, with car brand types and colors recorded using a Google form.  
23 entries were collected. The data is analysed using R and is also visualised below.


```{r}
# Load my csv file
logged_data <- read_csv("https://docs.google.com/spreadsheets/d/e/2PACX-1vQ3vuqzd-x--wlYthlk6a3hyA8P_jO8eoAe_6t9VqhstOihY99kkFqjtYFzBmFskABWhy7HYZKt6_W2/pub?output=csv")

# Renaming the variables
latest_data <- logged_data %>%
  rename(
    brand = 'What car brand did you see?',
    type = 'What type of brand is this?',
    color = 'What was the color of the car?',
    count = 'How many cars of this brand did you see today?'
  )

# Simplify the type column for plots
latest_data <- latest_data %>%
  mutate(type_short = case_when(
    str_detect(type, "Japanese") ~ "Japanese",
    str_detect(type, "German") ~ "German",
    str_detect(type, "Korean") ~ "Korean",
    str_detect(type, "American") ~ "American",
    str_detect(type, "Other") ~ "Other",
    str_detect(type, "Not sure") ~ "Not sure",
    TRUE ~ "Unknown"
  ))


# Summary
mean_count <- mean(latest_data$count, na.rm = TRUE)
max_count <- max(latest_data$count, na.rm = TRUE)


```
The **average** number of cars of the same brand seen was `r round(mean_count, 2)` and the **maximum** observed was `r max_count`.

```{r}
# Charts
ggplot(latest_data, aes(x = type_short)) +
  geom_bar() +
  labs(title = "Car Brands Observed", x = "Brand Type", y = "Count")
```


```{r}
ggplot(latest_data, aes(x = color)) +
  geom_bar() +
  labs(title = "Car Colors Observed")


```
